Robotic Cart System

### 2021-04-07 parts/30-customized_parabolic_reflector_array.tex

%----------------------------------------------------------------------
\section{Reflector Construction}
%----------------------------------------------------------------------
The reflector dishes were created using a 3D printer. After printing, the dishes were lined with reflective foil tape

>>>>

%----------------------------------------------------------------------
\section{Reflector Construction}
%----------------------------------------------------------------------
With the recent advancements in 3D printing technology, it is not difficult to create an object with a parabolic shape. In this project, the reflector dishes were created using a 3D printer. The reflector array was designed to be modular, where the dishes, top plate, and bottom frame were printed separately. After printing, the dishes were lined with foil tape to provide the reflective surface to focus the signals onto the antenna of the XBee. A layer of foil tape was also placed on the top plate to provide a ground plane for the XBee. The parts were then fastened together using M3 screws and nuts.
